Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-04 programlogic.tex
+

  \item Page Map Level-4 Translation (L4): Address translation, handling the first level (to get the PML4E entry) itself by calculating the offset (\textsf{CR3}$|^{12}$) and frame (PML4E$|^{52}$) via masking with the root address space address currently stored in \textsf{CR3}.

>>>>

  \item Page Map Level-4 Translation (L4): Address the first level address translation to get the PML4E entry in Figure \ref{fig:pagetables} by using the masks(\textsf{va}$|^{52}$(\textsf{CR3}) to get the starting address of the PML4 table and using the offset mask \textsf{va}$|^{12}$(\textsf{CR3}). It is worth noting that our offset indices are 12 bits as all physical memory pointsto assertions has to satisfy being \textsf{\textit{aligned}}, e.g. [47-39] plus 3 alignment bits in Figure \ref{fig:pagetables}. 
